# Continent {data-navmenu="Psychology"}

## Row 1 {data-width=2150} {.tabset .tabset-fade}

### Waffle plot of journal paper percentages, by continent (each square = 1% of data) {data-height=680}

```{r continent_waffle_overall_psychology}
articles.df4_psych <- articles.df4 %>% 
  filter(field == "psychology")

waffle_continent(articles.df4_psych, citation, citation_size = 7)

```



### Table of journal paper percentages, by continent

```{r, continent_table_psychology}
table_continent(articles.df4_psych)

```

> \* Percentages are calculated after excluding missing values. The *Missing* column shows the real percentage of missing values.

# Continent, by Year {data-navmenu="Psychology"}

## Row 1 {data-width=800} {.tabset .tabset-fade}

### Scatter plot of journal paper percentages, by continent and year {data-height=680}

```{r, continent_scatter_overall_psychology}
scatter_continent_year(articles.df4_psych, 
                       method = "loess",
                       ymin = 0,
                       ymax = 100,
                       yby = 20,
                       citation = citation2)

```



### Table of journal paper percentages, by continent

```{r, continent_table_journal_year_psychology}
table_continent_year(articles.df4_psych)

```

> \* Percentages are calculated after excluding missing values. The *Missing* column shows the real percentage of missing values.

# Continent, by Journal {data-navmenu="Psychology"}

## Row 1 {.tabset .tabset-fade}

### Waffle plot of journal paper percentages, by continent and journal (each square = 1% of data) {data-height=680}

```{r continent_table_journal_figure_psychology}
waffle_continent_journal(articles.df4_psych, citation)

```



### Table of journal paper percentages, by continent and journal

```{r continent_table_journal_psychology}
table_continent_journal(articles.df4_psych)

```

> \* Percentages are calculated after excluding missing values. The *Missing* column shows the real percentage of missing values.

# Country {data-navmenu="Psychology"}

## Row 1 {data-width=800} {.tabset .tabset-fade}

### Waffle plot of journal paper percentages, by country (each flag = 1% of data) {data-height=680}

```{r country_table_overall_psychology, fig.width=4.5, fig.height=4.5}
waffle_country(articles.df4_psych, citation, citation_size = 7)

```



### Table of journal paper percentages, by country

```{r country_table_journal_psychology}
table_country(articles.df4_psych)

```

> \* Percentages are calculated after excluding missing values. The *Missing* row shows the real percentage of missing values.

# Country, by Year {data-navmenu="Psychology"}

## Row 1 {.tabset .tabset-fade}

### Scatter plot of journal paper percentages, by country and year {data-height=680}

```{r, country_series_year_psychology}
scatter_country_year(articles.df4_psych, 
                     method = "lm",
                     ymin = 0,
                     ymax = 100,
                     yby = 20,
                     citation = citation2)

# Include flags on scatter plot
# Note: doesn't work with ggplotly it seems
# library(ggflags)
# df.country.year %>%
#   mutate(year = as.numeric(year),
#          country = countrycode(country, "country.name", "genc2c"),
#          country = tolower(country),
#          country = as.factor(country)) %>%
#   nice_scatter(
#              predictor = "year",
#              response = "percentage",
#              group = "country",
#              colours = colors,
#              method = "lm",
#              groups.order = "decreasing",
#              ytitle = "% of All Papers") + 
#   geom_flag(aes(country = country)) +#%>%
#   scale_country(aes(country = country)) #%>%
  #ggplotly(tooltip = c("x", "y"))

# Time series dygraph 
# dygraph_year(articles.df4_psych)
# dygraph_year(articles.df4_psych, "country")

```



### Table of journal paper percentages, by country and year

```{r, country_table_year_psychology}
table_country_year(articles.df4_psych)

```

> \* Percentages are calculated after excluding missing values. The *Missing* column shows the real percentage of missing values.

# Country, by Journal {data-navmenu="Psychology"}

## Row 1 {data-width=800} {.tabset .tabset-fade}

### Waffle plot of journal paper percentages, by continent and journal (each square = 1% of data) {data-height=680}

```{r country_table_journal_figure_psychology}
waffle_country_journal(articles.df4_psych, citation)

```



### Table of journal paper percentages, by country and journal

```{r country_table_journal2_psychology}
table_country_journal(articles.df4_psych)

```

> \* Percentages are calculated after excluding missing values. The *Missing* column shows the real percentage of missing values.
