# Continent {data-navmenu="Economics"}

## Row 1 {data-height=600}

### Waffle plot of journal paper percentages, by continent (each square = 1% of data)

```{r continent_waffle_overall_economics, fig.height = 4}
data_econ <- data %>% 
  filter(field == "economics")

waffle_continent(data_econ, citation, citation_size = 7)

```

## Row 2 {data-height=600}

### Table of journal paper percentages, by continent {data-width=1000}

```{r, continent_table_economics}
table_continent(data_econ)

```

```{r, results="asis"}
cat(instructions_table)
```

# Continent, by Year {data-navmenu="Economics"}

## Row 1 {data-height=700}

### Scatter plot of journal paper percentages, by continent and year {data-width=1460}

```{r, continent_scatter_overall_economics}
scatter_continent_year(data_econ, 
                       method = "loess",
                       citation = citation2)

```

```{r, results="asis"}
cat(instructions_figure)
```

## Row 2 {data-height=600}

### Table of journal paper percentages, by continent {data-width=1000}

```{r, continent_table_journal_year_economics}
table_continent_year(data_econ)

```

```{r, results="asis"}
cat(instructions_table)
```

# Continent, by Journal {data-navmenu="Economics"}

## Row 1 {data-height=1000}

### Waffle plot of journal paper percentages, by continent and journal (each square = 1% of data) {data-height=680}

```{r continent_table_journal_figure_economics}
waffle_continent_journal(data_econ, citation)

dictio <- journal_field %>% 
  filter(field == "economics") %>% 
  mutate(dictio = paste0(journal_abbr, ": ", journal)) %>% 
  distinct(journal_abbr, .keep_all = TRUE) %>% 
  pull(dictio) %>% 
  sort() %>%
  toString()

```

> *Note*. `r dictio`

## Row 2 {data-height=680}

### Table of journal paper percentages, by continent and journal {data-width=1000}

```{r continent_table_journal_economics}
table_continent_journal(data_econ)

```

```{r, results="asis"}
cat(instructions_table)
```

# Country {data-navmenu="Economics"}

## Row 1 {data-height=700}

### Waffle plot of journal paper percentages, by country (each flag = 1% of data)

```{r country_table_overall_economics, fig.width=4.5, fig.height=4.5}
waffle_country(data_econ, citation, citation_size = 7)

```

## Row 2 {data-height=650}

### Table of journal paper percentages, by country {data-width=1000}

```{r country_table_journal_economics}
table_country(data_econ)

```

```{r, results="asis"}
cat(instructions_table)
```

# Country, by Year {data-navmenu="Economics"}

## Row 1 {data-height=700}

### Scatter plot of journal paper percentages, by country and year {data-width=1460}

```{r, country_series_year_economics}
scatter_country_year(data_econ, 
                     method = "loess",
                     citation = citation2)

# Include flags on scatter plot
# Note: doesn't work with ggplotly it seems
# library(ggflags)
# df.country.year %>%
#   mutate(year = as.numeric(year),
#          country = countrycode(country, "country.name", "genc2c"),
#          country = tolower(country),
#          country = as.factor(country)) %>%
#   nice_scatter(
#              predictor = "year",
#              response = "percentage",
#              group = "country",
#              colours = colors,
#              method = "lm",
#              groups.order = "decreasing",
#              ytitle = "% of All Papers") + 
#   geom_flag(aes(country = country)) +#%>%
#   scale_country(aes(country = country)) #%>%
  #ggplotly(tooltip = c("x", "y"))

# Time series dygraph 
# dygraph_year(data_econ)
# dygraph_year(data_econ, "country")

```

> *Note*. The plot only shows the top seven countries for visualization purposes.

```{r, results="asis"}
cat(instructions_figure)
```

## Row 2 {data-height=650}

### Table of journal paper percentages, by country and year {data-width=1000}

```{r, country_table_year_economics}
table_country_year(data_econ)

```

```{r, results="asis"}
cat(instructions_table)
```

# Country, by Journal {data-navmenu="Economics"}

## Row 1 {data-height=700}

### Waffle plot of journal paper percentages, by continent and journal (each square = 1% of data) {data-height=680}

```{r country_table_journal_figure_economics}
waffle_country_journal(data_econ, citation)

```

> *Note*. The plot only shows the top seven countries for visualization purposes. `r dictio`

## Row 2 {data-height=680}

### Table of journal paper percentages, by country and journal {data-width=1000}

```{r country_table_journal2_economics}
table_country_journal(data_econ)

```

```{r, results="asis"}
cat(instructions_table)
```

# Journal, by Year {data-navmenu="Economics"}

## Row 1 {data-height=10000}

### Scatter plot of journal paper percentages, by continent and year {data-width=1460}

```{r, journal_scatter_overall_economics}
list.plots <- lapply(unique(
  data_econ %>% 
    filter(
      journal != 
        "African Journal of Agricultural and Resource Economics") %>% 
    pull(journal)), \(x) {
  zz <- scatter_continent_year(data_econ %>% 
                           as.data.frame() %>% 
                           filter(journal == x), 
                         method = "loess",
                         text_size = 11)
}) %>% 
  setNames(unique(
  data_econ %>% 
    filter(
      journal != 
        "African Journal of Agricultural and Resource Economics") %>% 
    pull(journal)))

# The journal below causes an unknown bug and is therefore excluded
# "African Journal of Agricultural and Resource Economics"

# list.plots[-1] <- lapply(list.plots[-1], \(x) {
#   x <- x + theme(legend.position = "none")
#   x
# })

gen <- names(list.plots)

my_y <- lapply(1:length(gen), function(i) {
  1 - (i - 1) / length(gen)
}) %>% unlist()

my_annotations <- lapply(seq_along(gen), \(x){
  list(x = 0.5, 
       y = my_y[x], 
       text = gen[x], 
       showarrow = FALSE, 
       xref = "paper", 
       yref = "paper", 
       font = list(size = 14))
})
  
subplot_obj <- plotly::subplot(
  list.plots, nrows = length(list.plots), shareX = TRUE) %>%
  plotly::layout(annotations = my_annotations)

# Remove redundant legends from all but the first plot
subplot_obj$x$data <- lapply(1:length(subplot_obj$x$data), function(i) {
  # Only remove legends from subsequent plots
  if (i > 6) {  # Adjusting index to correspond to legend settings
    subplot_obj$x$data[[i]]$showlegend <- FALSE  # Remove legend from others
  }
  return(subplot_obj$x$data[[i]])
})

# Render the modified subplot
subplot_obj

```

```{r, results="asis"}
cat(instructions_figure)
```

## Row 2 {data-height=600}

### Table of journal paper percentages, by continent {data-width=1000}

```{r, table_journal_year_economics}
table_journal_year(data_econ)

```

```{r, results="asis"}
cat(instructions_table)
```
